Challenges in Developing Great Quasi-Monte Carlo Software

### 2023-03-14 MCQMC2022ChallengesQMCSoftwareArticle.tex
sc: move unit test discussion from Section 6 to Section 4

@@

Great software should be stored in a repository, where the latest version can be downloaded.  There should be documentation that guides the user through installation and explains the library's features.  Demos are crucial for showing how the software works and for providing a template for new users to write their own code.  Tutorials help newcomers to QMC understand its advantages. Blogs educate a wider audience and enlarge our QMC community.  A suite of unit tests should be run regularly to ensure that new features do not introduce bugs.\SCComment{Move the last sentence to section on Correct} There should be a place for users to report bugs and make feature requests.

>>>>

\SCComment{The above examples and discussion also underscore the importance of continuous testing in QMC software development. This involves creating a comprehensive test suite that covers a wide range of scenarios and input parameters. Additionally, QMC software should be benchmarked against known results to ensure that it is both accurate and efficient.}

@@

Great software should be stored in a repository, where the latest version can be downloaded.  There should be documentation that guides the user through installation and explains the library's features.  Demos are crucial for showing how the software works and for providing a template for new users to write their own code.  Tutorials help newcomers to QMC understand its advantages. Blogs educate a wider audience and enlarge our QMC community.  There should be a place for users to report bugs and make feature requests.
